\documentclass[]{letter}

\begin{document}
Dear Sir / Madam,

We would like to submit our paper, entitled \textbf{``FaceLift: A transparent deep learning framework to beautify urban scenes''}, to the Royal Society Open Science journal.

Our paper attempts at answering the question ``Can deep learning help urban planners/designers, design better cities?''. In our paper, we develop a deep learning driven framework that can learn about perception of aesthetic qualities of urban spaces using a crowd sourced opinion, and use this knowledge to suggest enrichments for beautifying existing urban spaces. 
But these suggestions need to be articulated in the language of practitioners and users of such a tool. To partly fix this gap, we develop a literature inspired set of metrics which could provide valuable insights to urban planners about the said suggestions for beautification. We develop computer vision based techniques to evaluate these metrics on the pipeline's suggestions, and validate them through an expert survey. We also do a separate crowd validation about the actual beautification process. Our framework shows promising results on both these validation surveys.

We believe this paper makes progress towards making deep learning tools accessible to urban designers, architects and urban activists. We hope that this paper is clear in its presentation of results, and that the content will be interesting to the readers of your journal. Please do not hesitate to ask any questions or clarifications if needed.

Thanking you

Sincerely

The Authors

\end{document}
